% !TeX root = ../main.tex

% 中英文摘要和关键字

\begin{abstract}
  本论文对动态社交网络图的生成算法进行了一系列研究，分析了动态社交网络图动态性的表现方式，将图结构特征的时序变化抽象为“事件”这一概念并对一些典型的事件进行建模与实现。在此基础上，设计实现了一个高效的动态图生成算法，允许用户定义分布特征、时序长度、社区结构、动态事件等配置信息，生成结果可以以多种存储格式进行存储，便于用户使用常见的图数据处理、可视化库进行后续处理。并且设计实现了一个完整的动态图生成管理系统，包括网页前端与后端两部分，使用户可以在网页上进行动态图的配置工作，并在网页端完成图生成与结果的可视化任务。

  本文的创新点主要有：
  \begin{itemize}
    \item 提出了用事件对动态图结构上的时序变化进行建模的方法；
    \item 提出了节点映射这一结构，并将其用于动态图生成中事件的执行过程；
    \item 设计并实现了一个完整的动态社交网络图生成管理系统。
  \end{itemize}

  % 关键词用“英文逗号”分隔
  \thusetup{
    keywords = {动态社交网络图, 事件, 生成, 管理系统},
  }
\end{abstract}

\begin{abstract*}
  This paper conducts a series of research on the generation algorithm of dynamic social network graphs and analyses the dynamic characteristics of the dynamic social network graph. This paper abstracts the temporal changes of the graph structure features as the concept of “events”, and models and implements some typical events. On this basis, an efficient dynamic graph generation algorithm is designed and implemented, which allows users to define configuration information such as distribution characteristics, time series length, community structure, dynamic events, etc. The generated results can be stored in a variety of storage formats, so that users can use common graphic data processing and visualization packages for subsequent processing. A complete dynamic graph generation management system is designed and implemented, which includes two parts, front-end and back-end. Users can configure the dynamic graph, complete the generation of graphs, and visualize the results on the web page.

  The main innovations of this paper are:
  \begin{itemize}
    \item A method for modeling temporal changes in the structure of dynamic graphs using events is presented.
    \item A node mapping structure is proposed and used for event execution in dynamic graph generation.
    \item A dynamic social graph generation management system is designed and completed.
  \end{itemize}

  \thusetup{
    keywords* = {dynamic social graph, events, generation, management system},
  }
\end{abstract*}
